Plotting simulated PCR results

### 2022-03-28 09--simulated_pcr_results.Rmd
saved output table for genus counts for primer binding sites

```{r}
t(table(binding_data[, c("genus", "forward")]))
t(table(binding_data[, c("genus", "reverse")]))
t(table(binding_data[, c("genus", "primer_pair")]))
```

>>>>

```{r}
(genus_bindings_forward <- t(table(binding_data[, c("genus", "forward")])))
(genus_bindings_reverse <- t(table(binding_data[, c("genus", "reverse")])))
(genus_bindings_pair <- t(table(binding_data[, c("genus", "primer_pair")])))
```

Lets save all that information in a table for future reference:

```{r}
genus_bindings_data <- rbind(
  cbind(type = 'forward', genus_bindings_forward),
  cbind(type = 'reverse', genus_bindings_reverse),
  cbind(type = 'pair', genus_bindings_pair)
)
genus_bindings_data <- cbind(primer = rownames(genus_bindings_data), genus_bindings_data)
rownames(genus_bindings_data) <- NULL
write_csv(as.data.frame(genus_bindings_data),
          file = file.path('results', 'genus_primer_binding_site_counts.csv'))
```
